Real-Time Adaptive Ultrasound Algorithms \vspace{0.5cm}

### 2013-12-06 ThesisJP/Background/background.tex
ThesisJP: Changed section layout.

\subsection{Volume rendering}

\subsection{Simulations}

@@

\section{Motivation and aims of study}
\label{sec:motivationAndAims}

\section{Thesis outline}

\section{Summary of presented work}

\subsubsection{Paper no. 1:\\
An Optimised GPU Implementation of the MVDR Beamformer for Active Sonar Imaging}

\vspace{0.3 cm}
{\it Submitted for review to IEEE Transactions on Oceanic Engineering.}
\vspace{0.3 cm}

Summary of paper...

\vspace{0.3 cm}
\emph{The work was a joint effort with PhD student ...}

\subsubsection{Paper no. 2:\\
Implementing Capon Beamforming on a GPU for Real-Time Cardiac Ultrasound Imaging}

\vspace{0.3 cm}
{\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, vol. XY, January 2014.}
\vspace{0.3 cm}

Summary of paper...

\vspace{0.3 cm}
\emph{The work was a joint effort with PhD student ...}

\subsubsection{Paper no. 3:\\
Capon Beamforming Applied on Moving Objects - An Analysis of Local Lateral Shift-Invariance}

\vspace{0.3 cm}
{\it Submitted for review to IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control.}
\vspace{0.3 cm}

Summary of paper...

\subsubsection{Paper no. 4:\\
Adaptive Volume Rendering of Cardiac 3D Ultrasound Images - Utilizing Blood Pool Statistics}

\vspace{0.3 cm}
{\it Proc. SPIE Medical Imaging 2012}
\vspace{0.3 cm}

Summary of paper...

\subsubsection{Paper no. 5:\\
Huygens on Speed: Interactive Simulation of Ultrasound Pressure Fields}

\vspace{0.3 cm}
{\it Proc. IEEE Ultrasonics Symposium 2012}
\vspace{0.3 cm}

Summary of paper...

\section{Discussion}

\section{Conclusion}

\section{Future work}

\section{Publication list}

\subsubsection{Papers included in the thesis}
\begin{enumerate}
	\item J. I. Buskenes, J. P. \AA{}sen, C.-I. C. Nilsen and A. Austeng, "An Optimised GPU Implementation of the MVDR Beamformer for Active Sonar Imaging", {\it Submitted for review to IEEE Transactions on Oceanic Engineering}.
	\item 
\end{enumerate}

\subsubsection{Conference proceedings}
\begin{enumerate}
	\item 
	\item 
\end{enumerate}

\subsubsection{Presentations and abstracts}
\begin{enumerate}
	\item
\end{enumerate}

>>>>

\section{Volume rendering}

\section{Simulations}

@@

### 2013-12-06 ThesisJP/Introduction/introduction.tex
ThesisJP: Changed section layout.

% Thesis introduction
% Author: Tore.
%

General introduction to ultrasound, GPUs etc...

\section {Ultrasound imaging}

\subsection{Basic beamforming}

\subsection{Adaptive Beamforming}

\subsection{Shift invariance and sampling}

\subsection{Volume rendering}

\subsection{Simulations}

\section{General purpose programming on graphics processing units}

@@

\vspace{0.3 cm}
{\it Submitted for review to IEEE Transactions on Oceanic Engineering.}
\vspace{0.3 cm}

@@

\vspace{0.3 cm}
{\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, vol. XY, January 2014.}
\vspace{0.3 cm}

@@

\vspace{0.3 cm}
{\it Submitted for review to IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control.}
\vspace{0.3 cm}

@@

\vspace{0.3 cm}
{\it Proc. SPIE Medical Imaging 2012}
\vspace{0.3 cm}

@@

\vspace{0.3 cm}
{\it Proc. IEEE Ultrasonics Symposium 2012}
\vspace{0.3 cm}

>>>>

@@

{\it Submitted for review to IEEE Transactions on Oceanic Engineering.}
\vspace{0.3 cm}

@@

{\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, vol. XY, January 2014.}
\vspace{0.3 cm}

@@

{\it Submitted for review to IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control.}
\vspace{0.3 cm}

@@

{\it Proc. SPIE Medical Imaging 2012}
\vspace{0.3 cm}

@@

{\it Proc. IEEE Ultrasonics Symposium 2012}
\vspace{0.3 cm}
